\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}



%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Hetav Pandya}}\\
	Toronto, CA $\cdot$ pandyahetav1@gmail.com $\cdot$ (416) 826-4057 $\cdot$ www.linkedin.com/in/hetav-pandya\\
\end{center}

%==== Education ====%
\header{Education}
\textbf{University of Toronto}\hfill Toronto, CA\\
Bachelor of Applied Science and Engineering, Computer Engineering \textit{GPA: 3.97} \hfill Sep 2019 - May 2024\\
\vspace{2mm}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{Intel Canada - [Data Center and AI Team]} \hfill Toronto, CA\\
\textit{Software Engineering Intern} \hfill May 2022 - May 2023\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Developed a netlist writer for upcoming Quartus Prime releases to support a new database model.
	\item Developed an automated testing framework to functionally verify netlist between different stages.
	\item Worked alongside the router team to create a fix for a business-critical customer issue affecting our top model Agilex FPGAs. 
\end{itemize}

\textbf{Bell Canada - [Big Data and AI Team]} \hfill Toronto, CA\\
\textit{Data Scientist Intern} \hfill May 2021 - Aug 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Data querying using Apache Spark, Hadoop, and Impala. Data exploration using Python.
	\item Converted Impala queries to Trino reducing the time taken by 60\% on average.
	\item Developed an automated system to detect potential flaws in new version releases, reducing detection time from 3 weeks to 15 minutes. Results were shared using MicroStrategy BI.
\end{itemize}
\textbf{General Motors Canada (GM)} \hfill Toronto, CA\\
\textit{Machine Learning Model Developer} \hfill May 2021 - July 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Worked on automating data collection pipeline with data pre-processing and image augmentation.
	\item Deployed an object detection model using transfer learning on ‘my\_ssd\_mobnet’.
	\item The model was optimized for real time detection with a mean Average Precision (mAP) of 0.7.
\end{itemize}
\textbf{Faculty of Information, University of Toronto} \hfill Toronto, CA\\
\textit{Data Analyst Research Intern} \hfill Jan 2021 - May 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Analyzed the effects of machine learning on the future path of job creation and disruption.
	\item Collected raw data from research conferences, package databases and via webscrapping.
    \item Pre-processed data and generated visualizations for further analysis.
\end{itemize}
% \textbf{Engineering Outreach, University of Toronto} \hfill Toronto, CA\\
% \textit{Software Content Specialist} \hfill Feb 2020 - May 2020\\
% \vspace{-1mm}
% \begin{itemize} \itemsep 1pt
% 	\item Designed the “Computer Imaging using Python” and the “Data Analytics using MATLAB” courses.
% 	\item The courses were made for the DEEP program, which is an educational program offered by UofT.
% \end{itemize}

\header{Skills}
\begin{tabular}{ l l }
	Programming Languages: & Python, C++, C, JavaScript, Go                                   \\
	Machine Learning:      & TensorFlow, PyTorch, OpenCV, Kubeflow                            \\
    Hardware Design:       & Verilog, ARM Assembly, Quartus Prime                             \\
	Data Analysis:         & Hive, Impala, Trino SQL, Power BI, MicroStrategy BI, Hadoop \\
	Project Management:    & JIRA, Confluence, Agile - SCRUM, Git, GitHub, Perforce           \\                               
\end{tabular}
\vspace{2mm}

\header{Extra Curriculars}
\vspace{1mm}

\textbf{UofT Engineering Society} \hfill Toronto, CA\\
\textit{ECE Board of Director Representative} \hfill April 2022 - April 2023\\
\vspace{-1mm}
\begin{itemize} \itemsep 0.5pt
	\item Elected to represent 700+ students at the highest level of governance in the student-run Engineering Society.
	\item As a Board Member, I collaborate with other representatives to make executive decisions about the operation of the Society that offers services to 6000+ students at the University of Toronto.
\end{itemize}

\textbf{GitHub Education Program} \hfill Toronto, CA\\
\textit{GitHub Campus Expert} \hfill September 2022 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 0.5pt
	\item Selected as one of the 65 new campus experts globally in the 2022 cohort.
    \item Part of the organizing team that hosted the first GitHub Field Day in Canada.
    \item Organized a workshop on transfer learning and several Open-Source workshops on campus.
\end{itemize}

\textbf{UofT Machine Intelligence Student Team} \hfill Toronto, CA\\
\textit{Co-President} \hfill July 2021 - July 2022\\
\vspace{-1mm}
\begin{itemize} \itemsep 0.5pt
	\item Managing a team of 180+ active members spread across nine departments using JIRA software.
	\item Driving collaboration with different clubs and organizations like the Engineering Hatchery, UCL Artificial Intelligence Society, AI@MIT, Harvard Open Data Project and many more.
    \item Collaborating with industry partners and professors for hosting events and workshops.
\end{itemize}

\header{Projects}
{\textbf{ECE-Hustler}} {\sl C language, ARM Assembly, DE1-SoC board} \hfill https://tinyurl.com/d38wrur3\\
In this game you are an ECE student in the 4th semester at UofT trying to dodge the hurdles we faced! It is an obstacle course compiled using the ARM processor and displayed on a VGA display.\\
{\textbf{E-Motion}} {\sl Python, OpenCV, Selenium} \hfill https://tinyurl.com/cyhtt8jr\\
A computer vision suite that enables users to play games, read e-books and listen to music using hand gestures. It secured the second place at UofT Hacks VIII\\
\vspace*{2mm}
{\textbf{COVID-19 InfoBot}} {\sl Python, Selenium, Speech Recognition} \hfill https://tinyurl.com/ub8uyavj\\
A voice assistant that provides users with credible and updated information regarding the COVID-19. It won the Wolfram award at the Hack\_The\_Virus Hackathon.\\
\vspace*{2mm}
% {\textbf{Machine Learning Data Bot}} {\sl Python, Selenium} \hfill https://tinyurl.com/rc46kkd2\\
% The ML databot auto generates image data sets through web scrapping, significantly reducing the cost and time required in manual data generation.\\
% \vspace*{2mm}
{\textbf{Hands2Ears}} {\sl Python, OpenCV, Speech Recognition} \hfill https://tinyurl.com/65ftaddu\\
A neural network model that helps converting sign language (ASL) to speech in real time. It was chosen as the Bloomberg Challenge winner and second best project in NSBE Hacks 2020.\\
\vspace*{2mm}
% {\textbf{Drowsy Driver Detector}} {\sl Python, OpenCV, Face Detection} \hfill https://tinyurl.com/rdjd57hh\\
% The program uses an eye detection to alert the driver if they are drowsy thereby preventing fatal crashes.\\
% \vspace*{2mm}
{\textbf{Personal Website}} {\sl HTML5, CSS3, Javascript} \hfill https://pandyah5.github.io/\\
A more detailed and informal description of who I am. Built using raw HTML, CSS and PHP from scratch.\\
\vspace*{1mm}
{\textbf{Magnum Opus}} {\sl Python, Neural Style Transfer, OpenCV} \hfill https://tinyurl.com/8j9hs2hx\\
My personal journey of finding “art in mathematics” and “mathematics in art”.\\
\vspace*{2mm}
% {\textbf{My Other Projects}}\hfill https://tinyurl.com/wd2c893h\\
% You can explore my other projects on Computer Vision, Digital Art, Data Analysis, Web Automation and Machine Learning.\\
% \vspace*{2mm}

\header{Awards}
\textbf{Microsoft Discover AI Challenge on AI Ethics - First Prize} \hfill Microsoft\\
Recognized for the AI Ethics Pipeline built during the Hackathon. \hfill June 2021\\
\vspace*{2mm}
\textbf{University of Toronto Dean’s Honor Award} \hfill University of Toronto\\
Awarded for my consistent academic standing above 3.5 GPA in all semesters. \hfill May 2021\\
\vspace*{2mm}
\textbf{UofT Hacks VIII - Second Prize} \hfill UofT Hacks\\
Recognized for my project E-Motion and my work on computer vision enabled remote monitoring and
control. \hfill Feb 2021\\
\vspace*{2mm}
\textbf{Edward S. Rogers Dept. of Computer Eng. Top Student Award} \hfill University of Toronto\\
Awarded for being amongst the top three students in the Department of Electrical and Computer
Engineering. \hfill Sept 2020\\
\vspace*{2mm}
\textbf{Wallberg Undergraduate Scholarship Award} \hfill University of Toronto\\
Awarded for being amongst the top four students in the Faculty of Engineering, based on academic
performance. \hfill Sept 2020\\
\vspace*{2mm}
\textbf{Wolfram Award} \hfill Hack The Virus Hackathon\\
Recognized for my project COVID-InfoBot based on speech controlled information system. \hfill Aug 2020\\
\vspace*{2mm}
\textbf{NSBE Hacks 2020 - Second Prize} \hfill NSBE UofT\\
Recognized for my project Hands2Ears, real time ASL to speech conversion. \hfill Feb 2020\\
\vspace*{2mm}
\textbf{Bloomberg First Time Hack Winner} \hfill Bloomberg\\
Recognized for my project Hands2Ears - \textquotedbl{}First Time Hack\textquotedbl{} sub-category at NSBE Hacks 2020. \hfill Feb 2020\\
\vspace*{2mm}
\textbf{State Topper} \hfill Central Board of Secondary Education\\
Awarded for receiving the highest grade in the province/state of Gujarat for the Annual Grade-12
Examination in India. \hfill March 2019\\
\vspace*{2mm}
\textbf{University of Toronto International Scholar’s Award Scholarship} \hfill University of Toronto\\
This prestigious award is provided to students who demonstrate excellence in academics and a strong desire to learn by participating in a wide range of extracurriculars. \hfill May 2019\\
\
\end{document}
